signalHsmm - a novel semi-Markov model of eukaryotic signal peptides

### 2015-06-18 paper.tex
added code for benchmark table

To provide the honest comparison, we trained our model on 2311 signal peptide-containing sequences deposited in Uniprot until 2010 year (an iteration of signalHsmm called signalHsmm-2010). The data set should correspond to the set used to train SignalP 4.1. Interestingly, our algorithm performed very well even if it was trained on a very small sets including only 336 sequences collected till 1987 year, just after the first method predicting signal peptide was published~\citep{1986vonheijnea}. The signalHsmm-1987 was able to very accurately predict a signal peptide, even better than predictors trained on richer data sets. It indicates that signalHsmm is very stable and is able to recover the structure of signal peptides from even very small data sets.

>>>>

To provide the honest comparison, we trained our model on 2311 signal peptide-containing sequences deposited in Uniprot until 2010 year (an iteration of signalHsmm called signalHsmm-2010). The data set should correspond to the set used to train SignalP 4.1. Interestingly, our algorithm performed very well even if it was trained on a very small sets including only 336 sequences collected till 1987 year, just after the first method predicting signal peptide was published~\citep{1986vonheijnea}. The signalHsmm-1987 was able to very accurately predict a signal peptide, even better than predictors trained on richer data sets. It indicates that signalHsmm is very stable and is able to recover the structure of signal peptides from even very small data sets~\ref{tab:bench2010}.

\begin{table}[ht]
\centering
\begin{tabular}{lrrrr}
  \toprule
Software name & AUC & Sensitivity & Specificity & MCC \\ 
  \midrule
signalP 4.1 (no tm) \citep{2011petersensignalp} & 0.9424 & 0.9720 & 0.9128 & 0.8859 \\ 
   \rowcolor[gray]{0.85}signalP 4.1 (tm) \citep{2011petersensignalp} & 0.9675 & 0.9579 & 0.9771 & 0.9353 \\ 
  PrediSi \citep{2004hillerpredisi} & 0.8959 & 0.9065 & 0.8853 & 0.7919 \\ 
   \rowcolor[gray]{0.85}Phobius \citep{2004klla} & 0.9515 & 0.9673 & 0.9358 & 0.9033 \\ 
  Philius \citep{2008reynoldstransmembrane} & 0.9376 & 0.9533 & 0.9220 & 0.8755 \\ 
   \rowcolor[gray]{0.85}signalHsmm-2010 & 0.9429 & 0.9393 & 0.8761 & 0.8166 \\ 
  signalHsmm-1989 & 0.9455 & 0.9486 & 0.8945 & 0.8440 \\ 
   \bottomrule
\end{tabular}
\caption{Comparison of Area Under the Curve, Sensitivity, Specificity and Matthews Correlation Coefficient for different classifiers.} 
\label{tab:bench2010}
\end{table}
